---
title: "UTM to Decimal Degrees"
author: "Erika Barthelmess"
date: "11/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Code for converting UTM coordinates to decimal degrees

In order to upload our camera data to the eMammal interface, we need to convert from the UTM camera coordinates to decimal degrees.  Here is the code to do so.

Code requires a text file with the camera names/forest locations as well as the UTM coordinates.

## Step 1.  Prepare the workspace
```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(readr)
```
## Step 2.  Pull in the data

Our data are stored in a text file.  

```{r}
DF <- read_csv("Camera info/SnapUSA.txt")
```

## Step 3. Load required packages for spatial data
```{r}
library(rgdal)
library(spatial)
```
## Step 4.  Do conversion

First we need to extract the two utm columns into a matrix:
```{r}
locs<-cbind(DF$POINT_X, DF$POINT_Y)
row.names(locs)<- 1:nrow(locs)
str(locs)
```
Now convert the matrix values into spatial points
```{r}
locs_crs<-CRS("+proj=utm +zone18 +north +datum=NAD83")
locs_sp<-SpatialPoints(locs, proj4string = locs_crs)
summary(locs_sp)
```
Now we can convert to lat/long
```{r}
lat_long<-spTransform(locs_sp, CRS("+proj=longlat +datum=WGS84"))
```
Now take a look
```{r}
summary(lat_long)
```
Now extract just the coordinates from teh spatial object
```{r}
lat_long$coords
```

