---
title: "View Cameras"
author: "Erika Barthelmess"
date: "11/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Code to make camera locations spatial and view them on a map

##Step 1.  Set up workspace
```{r}
rm(list = ls())
library(dplyr)
library(ggplot2)
library(readr)
```
## Step 2.  Pull in the data
```{r}
DF <- read_csv("Camera info/snapshot_lat_long.txt")
```

## Step 3. Load required packages for spatial data
```{r}
library(rgdal)
library(sp)
```
Now let's rename the POINT_X and POINT_Y columns to "Long" and "Lat"

```{r}
library(plyr)
DF<-rename(DF, c("POINT_X"="Long", "POINT_Y" = "Lat"))
```

## Step 4. 
Convert DF to spatial data and set projection
```{r}
coords<-SpatialPoints(DF[c("Long", "Lat")], proj4string=CRS("+proj=longlat +datum=WGS84"))
DF<-SpatialPointsDataFrame(coords, DF)


```
## Now plot
```{r}
cameras<-plot(DF)
cameras
```
Provides basic plot of locations.



Let's use the leaflet package to get a fancy plot that shows us where the cameras are relative to the landscape and political boundaries.

```{r}
library(leaflet)
```
Now get the map midpoint
```{r}
mid_long<-median(DF$Long)
mid_lat<-median(DF$Lat)
map<-leaflet(data = DF,options = leafletOptions(minZoom = 0, maxZoom = 18)) 
setView(map, mid_long, mid_lat, zoom = 10)
map %>% addMarkers(lat = ~Lat, lng = ~Long) %>% addTiles()
```
It worked!

Now let's see if we can add a popup that identifies the camera number
Requires htmltools package
```{r}
library(htmltools)
DF$Camera_Num<-as.character(DF$Camera_Num)#because addMarkers label requires chr
map %>%  addTiles() %>% addMarkers(lat = ~Lat, lng = ~Long, label= ~htmlEscape(Camera_Num)) 

```


